The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
caribou socioecology section

## Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on social (visual and auditory perception), spatial (habitat
type), and temporal (seasonal). Caribou are gregarious ungulates with
fission-fusion dynamics [@Lesmerises_2018] that display temporal and spatial
variation in social networks [@Peignier_2019]. In winter, caribou dig holes in
the snow, termed craters, to access forage [@Bergerud_1974]. As a result,
caribou tend to occupy and re-use craters once they are established and there is
considerably less access to forage than when the landscape is snow-free.
Importantly, craters exist on the landscape at multiple scales: the crater scale
(a single crater), the feeding area scale (multiple craters in close proximity),
and the winter range scale (all craters within an individual’s range)
[@Mayor_2009]. The distribution of forage for caribou is therefore seasonally
heterogeneous, with greater access in snow-free seasons compared to winter as
well as spatially heterogeneous in winter because the distribution of craters on
the landscape varies meaning that access to vegetation in winter is highly
variable for caribou. We therefore partitioned data into two discrete seasons:
summer (3 August - 20 September) and winter (1 January – 17 February) based on
caribou socioecology [@Peignier_2019].

>>>>

## Caribou socioecology
Here, we use caribou as a case study to develop scale-dependent multilayer
networks based on predicted social (visual and auditory perception), spatial
(habitat type), and temporal (seasonal) scales. Caribou are gregarious ungulates
with fission-fusion dynamics [@Lesmerises_2018] that display temporal and
spatial variation in social networks [@Peignier_2019]. In winter, caribou dig
holes in the snow, termed craters, to access forage [@Bergerud_1974]. Cratering
is presumed to be a costly behaviour and as a result, caribou tend to occupy and
re-use craters once they are established and there is considerably less access
to forage than when the landscape is snow-free. Importantly, craters exist on
the landscape at multiple scales: the crater scale (a single crater), the
feeding area scale (multiple craters in close proximity), and the winter range
scale (all craters within an individual’s range) [@Mayor_2009]. The distribution
of forage for caribou is therefore seasonally heterogeneous because the
distribution of craters on the landscape varies meaning that access to
vegetation in winter is highly variable for caribou. Caribou therefore have
greater access to forage in snow-free seasons. We  partitioned data into two
discrete seasons: summer (3 August - 20 September) and winter (1 January – 17
February) based on caribou socioecology [@Peignier_2019].
